---
title: "R Notebook"
output: html_notebook
---

Create a vector called stock_prices with the following data points: 23, 27, 23, 21, 34, 24, 25, 30, 37, 30.

Create a vector called day_of_week, which repeats Monday to Friday twice. i.e. ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’, ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’.

```{r}
stock_prices<-c(23,27,23, 21,34,24,25,30,37,30)
```

```{r}
rep_day_of_week <- rep(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), 2)
```

```{r}
day_of_week<-c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
```


2.Create a vector called day_of_week_factor, which has the same data as day_of_week, but as a factor.

Created a vector called named_stock_prices, which is stock prices, named with days of the week.

```{r}
day_of_week_factor<- factor(day_of_week)
```

```{r}
named_stock_prices<- stock_prices
names(named_stock_prices) <- day_of_week
named_stock_prices
```


3. Make a data frame called stock_data with the stock price and day of the week information in it, and View the result.

```{r}
stock_data<-data.frame(day_of_week, stock_prices)
stock_data
```

4.Make a matrix called stock_matrix with 2 columns and 5 rows, so that the stock prices for one week are the first column, and the stock prices for the second week are the second column.

```{r}
stock_matrix<-matrix(stock_data$stock_prices, nrow = 5, ncol=2, byrow=FALSE)
stock_matrix
```

Make a list called stock_list with named elements, that has the individual vectors of stock_prices and day_of_week along with the matrix you made in question 4.
```{r}
stock_list <- list(stock_prices,day_of_week, stock_matrix)
stock_list

```


2 Part 2
In this part of the homework you will practice selecting elements from vectors, data frames, matrices and lists.

Select the 4th, 5th and 6th stock prices from stock_prices.

Select the stock prices greater than 30 from stock_prices.

```{r}
stock_prices[4]
stock_prices[5]
stock_prices[6]
```
```{r}
stock_prices[stock_prices>30]
```
4. Select the day_of_week column from the stock_data data frame.
```{r}
dow_col <- stock_data[1]
dow_col
```


Select the rows of the stock_data data frame where the stock_prices is less than 25.
```{r}
stock_rows<- stock_data[2]
stock_rows[stock_rows< 25]


```

3. Select the 1st column of the matrix

```{r}
stock_data[,1]
```


Select the 3rd row of the matrix
```{r}
stock_data[3,]
```


Select the 3rd element in the 1st row of the matrix
null because there are only 2 elements day and price...
```{r}
stock_data[1,3]
```

Select the matrix stock_matrix from stock_list.

```{r}
stock_list[3]
```

```{r}
install.packages("tidyquant")
library("tidyquant")
```